\bf Focusing on Fast Neural Network Inference

### 2018-05-15 wnmt.2018/wnmt.tex
cast

We desribe the main enhancements to Amun since the original public in 2016.

@@

\subsection{Softmax and Beam Search Kernel Fusion}

@@

/////////////////////////////////////////////////////////////////////////////////////

@@

Firstly, the number of classes in many deep-learning applications is small. However, the number of classes in NMT models is typically in the tens or hundreds of thousands, corresponding to the vocabulary size of the output language. For example, ~\citet{sennrich-haddow-birch:2016:P16-12} experimented with target vocabulary sizes of 60,000 and 90,000 sub-word units. This makes the output layer of NMT models very computationally expensive. Figure~\ref{fig:pie-time-europarl} shows the breakdown of amount of time during translation our NMT system; nearly 70\% of the time is involved in the output layer. We will look at optimizations which explicitly target the output layer.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-europarl.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (Europarl test set)}
\label{fig:pie-time-europarl}
\end{figure}

Secondly, the use of mini-batching is critical for fast model inference. However, mini-batching does not take into account variable sentence lengths which decrease the actual number of input or output sentences that are processed in parallel, negating the benefit of mini-batching. This can be partially reduced in the encoding with \emph{maxi-batching}, i.e. pre-sorting sentences by length before creating mini-batches with similar length source sentences. However, maxi-batching can introduce unacceptable delay in response for online applications as the input are not processed in the order they came. It is also not appropriate for applications where only the output lengths varies, for example, image captioning.

>>>>

We desribe the main enhancements to Amun since the original 2016 publication.

@@

The use of mini-batching is critical for fast model inference. However, a percularity

However, mini-batching often does not take into account variable sentence lengths which decrease the actual number of input or output sentences that are processed in parallel, negating the benefit of mini-batching. This can be partially reduced in the encoding with \emph{maxi-batching}, i.e. pre-sorting sentences by length before creating mini-batches with similar length source sentences. However, maxi-batching can introduce unacceptable delay in response for online applications as the input are not processed in the order they came. It is also not appropriate for applications where only the output lengths varies, for example, image captioning.

The number of classes in many deep-learning applications is small but this is often not the case with NMT models. For example, ~\citet{sennrich-haddow-birch:2016:P16-12} experimented with target vocabulary sizes of 60,000 and 90,000 sub-word units. This makes the output layer of NMT models very computationally expensive. Figure~\ref{fig:pie-time-europarl} shows the breakdown of amount of time during translation our NMT system; nearly 70\% of the time is involved in the output layer. We describe the steps to fuse the operations to improve efficiency.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time-europarl.png}} 
\end{tabular}
\caption{Proportion of time spent during translation (Europarl test set)}
\label{fig:pie-time-europarl}
\end{figure}

@@

////////////////////////////////////////////////////////////////

@@
